\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{pdfauthor   = DJD,
            pdftitle    = CGMP Bylaws,
            pdfsubject  = bylaws based on https://www.tucsonaz.gov/files/integrated-planning/G._SAMPLE_BYLAWS_FINAL.pdf
            }

\title{\textbf{{\Large Community Garden Mapping Project Bylaws \\ Rosemallow Chapter - Tallahassee, FL}}}
\author{Chairman Daniel Dom\'inguez}
\date{\today}

\begin{document}

\maketitle

\section*{ Article I. Name \& Boundaries }
\begin{enumerate}[label=(\Alph*)]
\item The name of the association shall be Community Garden Mapping Project: Rosemallow Chapter.
\item The association shall encompass the area of Tallahassee, FL. \textbf{BoundingBox( 362288.43,  706416.84 :
388244.20,  725136.09 )}
\end{enumerate}

\section*{Article II. Membership}
\begin{enumerate}[label=(\Alph*)]
\item The membership of this association shall be voted on by members following a request to, and then recommendation from a nominating committee. A 2/3rds majority vote is required to grant membership. 
\item Members will sign an affirmation of dedication that outlines their commitment of support. 
\item A voting member shall be an individual or group within the boundaries of the organization. Each voting member is entitled to one vote.
\item Membership shall not be denied on the basis of views or opinions contrary to the goals and purposes of the association.
\end{enumerate}

\section*{Article III. Officers}
\paragraph{}A term of office shall begin at the close of the annual meeting. The officers of the association shall be the Chairperson, a Vice Chairperson, and a Secretary/Treasure, if deemed appropriate. The officers of the association will comprise the board of directors.

\paragraph{} Absent officers, the founding member is seated as the Chairperson.

\begin{enumerate}[label=(\Alph*)]

\item \textbf{The Chairperson} shall call and preside at all meetings, shall act for and on behalf of the membership of the association, shall appoint any special committees necessary for the operation of the association business and shall act as official spokesperson for the association.

\item \textbf{The Vice Chairperson} shall, in the absence of the chairperson,
assume all of the duties of that office and shall be responsible for publicity and notifications of meetings of the association.

\item \textbf{The Secretary/Treasurer} shall keep a permanent record of all formal meetings and all legal documents and legal transactions of the association. This officer shall transcribe the minutes of each meeting and shall maintain a file copy available to members and volunteers. This officer shall keep all financial receipts and a permanent record of all financial business of the association. An up-to-date financial report shall be submitted at each meeting. 

\item Any officer can be removed from office by a 2/3rds majority vote of the members and chairperson after a special meeting has been requested at least five (5) business days in advance. Adequate notice must be provided to all members for meetings involving the recall of officers.

\end{enumerate}
\section*{Atrticle IV. Committees}
\begin{enumerate}[label=(\Alph*)]
\item The Chairperson shall have the power to appoint committees as necessary to implement the purposes of the charter.
\item The Chairperson shall be an ex-officio member of all committees.
\end{enumerate}

\section*{Article V. Meetings}
\paragraph{}An annual meeting shall be held during the month of January at a time and place designated by the chairperson.
\begin{enumerate}[label=(\Alph*)]
\item Not less than 51\% percent of the voting members shall have the privilege of petitioning a special meeting at any time.
\item The voting members present shall constitute a quorum.
\item At least a three (3) days notice shall be provided in advance of any association meeting. Every effort will be made to notify all interested parties and members of the association of upcoming meetings either by phone, e-mail, meeting notices, bulletin boards, newsletters, or announcements at regularly scheduled meetings.
\item Meetings shall be public and open to any interested persons.
\end{enumerate}

\section*{Article VI. Nomination, Election, Annual Reports and Installation of officers.}
\begin{enumerate}[label=(\Alph*)]
\item Nominations of officers shall be made from the floor at the annual meeting or slate presented from a nominating committee.
\item Election of officers shall be held 1-2 meetings following the nominations.
\item Upon installation of new officers, all documents, records, and any materials pertaining to the duties of the office as designated in the bylaws which are in the possession of the outgoing officers shall be submitted to the newly elected counterpart within five (5) days of the installation.
\item Any officer vacancies occurring during the year shall be filled by appointment by the board.
%\item Any officer may be removed from office for cause\footnote{For Cause means: (a) a material breach of this charter; (b) the officers willful failure to adhere to any written association policy if the officer has been given a reasonable opportunity to comply with such policy or cure their failure to comply (which reasonable opportunity must be granted during the 10-day period preceding termination)} by a majority vote of members.
\end{enumerate}

\section*{Article VII. Fiscal Responsibility}
\begin{enumerate}[label=(\Alph*)]
\item Expenditure of funds of the association may not be made without the signatures of
at least the chairperson and treasurer.
\item Financial records and funds of the association shall be audited at least once a year
by a committee of at least two members appointed by the chairperson prior to a new treasurer’s
taking office.
\end{enumerate}


\section*{Article VIII. Amendment of Bylaws}
\begin{enumerate}[label=(\Alph*)]
\item A unanimous vote by the board of directors is required for each change or amendment to the bylaws.
\item Proposed amendments shall be sent to all members at least five (5) working days in advance of the meeting where action is to be taken or shall be read at the presiding meeting.
\end{enumerate}

\section*{Article IX. General}
\begin{enumerate}[label=(\Alph*)]
\item Basic parliamentary procedure governs the
association, the board of directors, and all subcommittees in all cases to which
they apply and do not conflict with the specific provisions of these bylaws or any
special rules that the association may adopt.
\item If any part of these bylaws or the application thereof is hereafter held invalid or
unenforceable, the remainder shall not be affected thereby, and only the affected
portions are declared eliminated
\item No officer, representative, spokesperson or member shall have any financial
liability of the association.

\end{enumerate}

\paragraph{Date Adopted}
\end{document}