\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{pdfauthor   = DJD,
            pdftitle    = CGMP Special Rules,
            pdfsubject  = Organization Rules
            }

\title{\textbf{{\Large Community Garden Mapping Project Special Rules \\ Rosemallow Chapter - Tallahassee, FL}}}
\author{Chairman Daniel Dom\'inguez}
\date{\today}

\begin{document}

\maketitle

\section*{ Article I. Name \& Boundaries }
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article II. Membership}
\paragraph{} Membership is not handed out. Therefore, members must appeal for membership and must adhere to the following rules.
\begin{enumerate}[label=(\roman*)]
\item Prospective members, set forth by a nominating committee, will need to read the CIA Sabotage Field Manual and pass a short test on the subject matter to qualify for membership.
\item Prospective members will produce and sign an affirmation of their commitment to the organization. 

\end{enumerate}

\section*{Article III. Officers}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Atrticle IV. Committees}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article V. Meetings}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article VI. Nomination, Election, Annual Reports and Installation of officers.}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article VII. Fiscal Responsibility}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article VIII. Amendment of Bylaws}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\section*{Article IX. General}
%\begin{enumerate}[label=(\Alph*)]
%\end{enumerate}

\end{document}